### 2023-05-08 README.Rmd
Prepare for 2.2.0 release

`r badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
`r badge_github_actions("nesscoder/fasano.franceschini.test")`
<!-- badges: end -->

@@

You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://CRAN.R-project.org) with:

@@

And the development version of the `fasano.franceschini.test` package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nesscoder/fasano.franceschini.test")
```

>>>>

`r badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("braunlab-nu/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
`r badge_github_actions("braunlab-nu/fasano.franceschini.test")`
<!-- badges: end -->

@@

You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://cran.r-project.org/) with:

@@

The development version of the `fasano.franceschini.test` package can be installed from Github with:

``` r
# install.packages("devtools")
devtools::install_github("braunlab-nu/fasano.franceschini.test")
```
